Halo alignments with large scale tidal and velocity fields

### 2013-02-27 paper/main.tex
new references

\citep{Libeskind2013} %various alignments

\citep{Faltenbacher2009} %galaxy alignments with mocks
\citep{Paz2008} %angular momentum alignments
\citep{Platen2008} %alignment in voids
\citep{Lee2007}%Obs. spin alignment

@@

They measure the sping alignment with each one of the
eigenvectors. With repecto to the first eigenvector $e_{1}$ there is
antialignement for masses $M>10^{12}$\Msun and alignment for masses
$<10^{12}$\Msun

>>>>

\citep{Libeskind2013} %various alignments
\citep{Libeskind2012} %varios alignments
\citep{Faltenbacher2009} %galaxy alignments with mocks
\citep{Paz2008} %angular momentum alignments
\citep{Platen2008} %alignment in voids
\citep{Lee2007}%Obs. spin alignment

@@

They measure the sping alignment with each one of the
eigenvectors. With repecto to the minor eigenvector $e_{1}$ there is
antialignement for masses $M>5\times10^{12}$\Msun and alignment for masses
$<5\times 10^{12}$\Msun. With respect to the intermediate eigenvector $e_2$
there is a strong alignment at high masses and no alignment for low
masses, with respecto the major eigenvector $e_{3}$ there is an
anti-alignment signal at all masses. The results from the Skeleton
algorithm are in perfect agreement with the results from the Tidal
web.  The transitional mass is weakly dependent on the smoothing scale,
varing between $1-5\times 10^{12}$\hMsun for smoothing scales between
  $1.0-5.0$\hMpc.
